Gradual Soundness: Lessons from Static Python

### 2021-10-27 ecoop-2022/paper.tex

Nom~\cite{mt-oopsla-2017} is foundational.
Thorn~\cite{wnlov-popl-2010} and StrongScript~\cite{rzv-ecoop-2015} are related.

@@

This is one of the main advantages of \SP{} over mypyc,
which implements type-directed optimizations for CPython
by compiling source code to C extension modules.

>>>>

Nom~\cite{mt-oopsla-2017} is foundational.

\citet{pmmwplck-oopsla-2013} core calculus for Python language, foundational.

Thorn~\cite{wnlov-popl-2010} and StrongScript~\cite{rzv-ecoop-2015} are related.

@@

Type systems for Python ...
mypy pyre pytype;
Reticulated;

Optimizing type systems for Python ...
Reticulated;
mypyc;
Developer experience is one of the main advantages of \SP{} over mypyc,
which implements type-directed optimizations for CPython
by compiling source code to C extension modules.
